Constant Error Tolerance Computational Fuzzy Extractors

### 2014-01-28 trunk/constantRate/ConstCompFuzzExt.tex
Adding outline for sampling construction

\begin{construction}
\label{cons:first construction}
Let $n$ be a security parameter and let $W = W_1,..., W_\ell$ be a distribution over $\zo^{\ell n}$.  Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^n$.  Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ %be an output equiprobable 
$(\neigh_t, \epsilon_{code})$-error-correcting code.  
We describe $\gen, \rep$ as follows:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\ell$
\item Sample $c\leftarrow C$.
\item For $i=1,..., \ell$:
\subitem If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
\subitem Else: Sample $r_i \leftarrow U_n$. 
\subsubitem Let $p_i = \mathcal{O}(I_{r_i})$.
\item Output $(c, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ 
\item For $i=1,..., \ell$:
\subitem If $p_i(w_i') = 1$: set $c_i' = 0$.
\subitem Else: set $c_i' = 1$.
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.15in}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

@@

\section{Discussion}
\label{sec:discussion}
Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.  Correction occurs for a small number of dimensions that are allowed to vary completely.  As described in \secref{sec:sec of construction}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).

@@

\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.  The first is that Hamming distance is over an alphabet of exponential size, which precludes use in some applications.  The second is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.  Lastly, we obtain only a single bit from each block of $W_i$ which seems sub optimum.
\bibliographystyle{alpha}
\bibliography{crypto}

>>>>

\begin{construction}
\label{cons:first construction}
Let $n$ be a security parameter and let $W = W_1,..., W_\ell$ be a distribution over $\zo^{\ell n}$.  Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^n$.  Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ be a
$(\neigh_t, \epsilon_{code})$-error-correcting code.  
We describe $\gen, \rep$ as follows:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\ell$
\item Sample $c\leftarrow C$.
\item For $i=1,..., \ell$:
\subitem If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
\subitem Else: Sample $r_i \leftarrow U_n$. 
\subsubitem Let $p_i = \mathcal{O}(I_{r_i})$.
\item Output $(c, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ 
\item For $i=1,..., \ell$:
\subitem If $p_i(w_i') = 1$: set $c_i' = 0$.
\subitem Else: set $c_i' = 1$.
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.15in}
\end{minipage} 
\end{tabular}
\end{center}
\end{construction}

@@

\subsection{Discussion}
\label{sec:discussion}
Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.  Correction occurs for a small number of dimensions that are allowed to vary completely.  As described in \secref{sec:sec of construction}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).

@@

\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.   The first is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.  Second, we obtain only a single bit from each block of $W_i$ which seems sub optimum.  Lastly, Hamming distance is computed over an alphabet of exponential size, which precludes use in some applications. We begin to address this weakness in the next section.

\section{Sample-then-Obfuscate}
\consref{cons:first construction} is a computational fuzzy extractor with $gap<0$.  In this section, we present a generalization of where the values being obfuscated are sampled from the blocks of the source, but blocks are not individually obfuscated.  This has two advantages, first it simplifies the type of sources we consider as we no longer need high entropy blocks.  Second, it allows us to decrease the size of each block from exponential to a super polynomial $2^{\log^c n}$ for some $c>0$.  Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.

\begin{construction}
\label{cons:sampling}
Let $n$ be a security parameter.
Let $Z$ be an alphabet where $|Z| = \omega(\poly(n))$, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$.  Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.  Let $\sample_\beta(\gamma)$ output a uniform subset of indices of $1,..., \gamma$ of size $\beta$. Let $\eta = \omega(\log n)$ be some function such that $\eta \log (Z) = \omega(\log n)$.  Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^\eta$.  Define $\gen, \rep$ as:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item Sample $c\leftarrow C$.
\item For $i=1,..., \ell$:
\begin{itemize}
\item Sample $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_\eta(\gamma)$
\item If $c_i = 0$: 
\subitem Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
\subitem Set $\rho_i = \mathcal{O}(I_{w_i})$.
\subitem Set $p_i = \rho_i, j_{i, 1},..., j_{i, \eta}$.
\item If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
\subitem Let $p_i = \mathcal{O}(I_{r_i}) j_{i,1},..., j_{i, \eta}$.
\end{itemize}
\item Output $(c, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ 
\item For $i=1,..., \ell$:
\begin{itemize}
\item Parse $p_i$ as $\rho_i, j_{i, 1},..., j_{i, \eta}$.
\item Set $v_i = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
\item If $\rho_i(w_i') = 1$ set $c_i' = 0$.
\item Else set $c_i' = 1$.
\end{itemize}
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.37in}
\end{minipage} 
\end{tabular}
\end{center}
\end{construction}

The main change in \consref{cons:sampling} is that the obfuscated values are concatenated alphabet symbols of $W$.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.  There is a crucial difference, our use of a computationally-secure primitive allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.  In the information-theoretic setting, it would be necessary to argue about the joint entropy of the obfuscated values.

As before we must show security and correctness of \consref{cons:sampling}.  For security, the main argument is that each of the $v_i$ created has enough entropy to be unguessable.  For correctness we must show that the probability for each symbol $v_i \neq v_i'$ is a small constant so that $c'$ will be corrected to $c$ with overwhelming probability.

\subsection{Security of \consref{cons:sampling}}
In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $v_i$ has entropy on its own.  From here security follows as the set of $V_1,..., V_\ell$ is a block-unguessable distribution and then overall security follows by \thref{thm:security of cons}.  Consider a source with entropy $\lambda$.  Then the expected entropy of 
\begin{align*}
\expe[\Hoo(V_i)] &=\expe[\text{entropy of each uniform }w_j] (\text{number of }w_j\text{ selected})\\
&=\frac{\lambda}{\gamma} \times \eta= \frac{\lambda \eta}{\gamma}.
\end{align*}
This value is super-logarithmic when $\lambda = \omega (\frac{\gamma \log n}{\eta})$.  Note this is independent of how the entropy is distributed between blocks.  In particular, we make no assumptions about particular blocks being unguessable, only about the overall entropy rate.  This is a much more natural condition for a source than \defref{def:block guessable}.  To show security we need the entropy of all $v_i$ to be $\omega(\log n)$ with overwhelming probability.  This follows by an argument from the locally computable extractor literature.

\begin{theorem}
\label{th:samp sec}
Let $n$ be a security parameter and let $Z$ be some super-polynomially size alphabet.  Let $W = W_1,..., W_\gamma$ be a distribution where each $W_i$ is over $Z$.  Let 
\[
\Hoo(W) = \omega\left(\frac{\gamma \log n}{\eta}\right),
\] 
then for all $i$ and for all values of $j_{1,1},..., j_{\ell, \eta}$ the distribution $\delta(V_i | j_{1,1},..., j_{\ell, \eta} , V'_i ) <\epsilon_{sam}$ where $\Hoo(V_i') = \omega(\log n)$.
\end{theorem}

\begin{corollary}
\label{cor:samp unguess}
Let $n, Z, W$ be as in \thref{th:samp sec}, then for all $j_{1,1},..., j_{\ell, \eta}$, $V | j_{1,1},..., j_{\ell,\eta}$ is $\epsilon_{sam}$ close to a $(\poly(n), \alpha = \omega(\log n), 0)$-block unguessable distribution.  In particular, If $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = 2\epsilon_{obf} + \ell(\epsilon_{sam} + 2^{-(\alpha-1)})$.
\end{corollary}
\begin{proof}
Direct result of \thref{th:samp sec}, \bnote{need a claim saying if all $W_i$ have entropy, we are block unguessable}, and \thref{thm:security of cons}.
\end{proof}

\bnote{something something about by sampling theory the prob of this being more than constant from expected value is negligible.}
\bnote{need to finish this}

\subsection{Correctness of \consref{cons:sampling}}
The argument that $1\rightarrow 0$ flips are extremely unlikely carries over from \consref{cons:first construction}.  In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.  Consider a single index $i$ and let $t$ be the number of errors between $w$ and $w'$.  Then 
\begin{align*}
\Pr[v_i = v_i' ] &= \Pr[w_{j_{i,1}} = w_{j_{i,1}}' \wedge ... \wedge w_{j_{i, \eta/|Z|}} = w_{j_{i, \eta}}']\\
&=\Pr[w_{j_{i,1}} = w_{j_{i,1}}'] \times ... \times \Pr[w_{j_{i, \eta/|Z|}} = w_{j_{i, \eta}}']\\
&=\left (1-\frac{t}{\gamma}\right)^{\eta}
\end{align*} 
This value is $\Theta(1)$ when $t = \Theta(\frac{\gamma }{\eta})$.
\bnote{finish, Chernoff, not far from expectation.}

\subsection{Discussion}
\bnote{need to write this once we have parameters in the two sections above.}
%As shown above we get security when $\lambda = \omega(\gamma \log n/\eta)$ and correctness when $t = \Theta(\gamma /\eta)$.  This yields:
%\begin{align*}
%gap &= \Hoo(W) -\log |B_t| \\
%&< \omega(\frac{\gamma  \log n}{\eta} ) - (\Theta(t \mu) + \log {\gamma \choose t})\\
%&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \mu^2}{\eta}))\\
%&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \log |Z|}{\eta}))\\
%&= \omega(\frac{\gamma \log n}{\eta})
%\end{align*}
%%Taking $\gamma = \Omega(n)$ and $\eta = \log^c n$ yields a negative $gap$.
%\bnote{finish}
\bibliographystyle{alpha}
\bibliography{crypto}
